\documentclass[../main.tex]{subfiles}


%\bibliography{cite}
\begin{document}
    \section*{REFERENCES}
 \addcontentsline{toc}{section}{REFERENCES}
\begingroup
\renewcommand{\section}[2]{} % Suppress the "References" title

\begin{thebibliography}{99}

% Poultry IoT & Monitoring Systems
\bibitem{ahmed2023smart}
M. M. Ahmed, E. E. Hassanien, and A. E. Hassanien, ``A smart IoT-based monitoring system in poultry farms using chicken behavioural analysis,'' \textit{Internet of Things}, vol. 25, p. 101010, 2024.

\bibitem{ojo2022internet}
R. O. Ojo, A. O. Ajayi, H. A. Owolabi, L. O. Oyedele, and L. A. Akanbi, ``Internet of Things and Machine Learning techniques in poultry health and welfare management: A systematic literature review,'' \textit{Computers and Electronics in Agriculture}, vol. 200, p. 107266, 2022.

\bibitem{godinho2025wireless}
A. Godinho, R. Vicente, S. Silva, and P. J. Coelho, ``Wireless Environmental Monitoring and Control in Poultry Houses: A Conceptual Study,'' \textit{IoT}, vol. 6, no. 2, p. 32, 2025.

\bibitem{chang2023iot}
Y.-S. Chang and L.-Y. Tu, ``Use of IoT Sensors to Build an Intelligent Monitoring and Control System for Poultry House Environment,'' \textit{Sensors and Materials}, vol. 35, no. 12, pp. 3997--4012, 2023.

\bibitem{lashari2023internet}
M. H. Lashari, S. Karim, M. Alhussein, A. A. Hoshu, K. Aurangzeb, and M. S. Anwar, ``Internet of Things-based sustainable environment management for large indoor facilities,'' \textit{PeerJ Computer Science}, vol. 9, p. e1623, 2023.

\bibitem{kamor2024poultry}
S. Kamor, M. M. S. Raihan, S. N. Alam, S. Saha, S. R. Bondhon, and N. Kaur, ``Poultry Farming in Future Using IoT,'' \textit{SSRN}, Tech. Rep., 2024. [Online]. Available: \url{https://ssrn.com/abstract=4491157}.

\bibitem{karun2024iot}
K. C. Karun, K. Subedi, S. Sharma, and P. Paneru, ``IoT based Smart Poultry Management System,'' \textit{IRO Journals}, 2024. [Online]. Available: \url{https://www.researchgate.net/publication/380119628_IoT_based_Smart_Poultry_Management_System}.

\bibitem{yourstory2018poultrymon}
YourStory, ``PoultryMon, an IoT-based device from MLIT is helping poultry farms improve efficiency,'' \textit{YourStory}, 2018. [Online]. Available: \url{https://yourstory.com/2018/08/poultrymon-iot-help-poultry-farms-improve-efficiency}. [Accessed: Jul. 27, 2025].

% Machine Learning & Prediction Methods
\bibitem{ji2025egg}
H. Ji, Y. Xu, and G. Teng, ``Predicting egg production rate and egg weight of broiler breeders based on machine learning and Shapley additive explanations,'' \textit{Poultry Science}, vol. 104, no. 1, p. 104458, 2025.

\bibitem{manikandan2025acoustic}
V. Manikandan and S. Neethirajan, ``Decoding Poultry Welfare from Sound---A Machine Learning Framework for Non-Invasive Acoustic Monitoring,'' \textit{Sensors}, vol. 25, no. 9, p. 2912, 2025.

\bibitem{mao2022distress}
A. Mao, C. S. E. Giraudet, K. Liu, I. De Almeida Nolasco, Z. Xie, Z. Xie, Y. Gao, J. Theobald, D. Bhatta, R. Stewart, and A. G. McElligott, ``Automated identification of chicken distress vocalizations using deep learning models,'' \textit{Journal of the Royal Society Interface}, vol. 19, no. 191, p. 20210921, 2022.

\bibitem{breiman2001rf}
L. Breiman, ``Random Forests,'' \textit{Machine Learning}, vol. 45, no. 1, pp. 5--32, 2001.

\bibitem{liu2008iforest}
F. T. Liu, K. M. Ting, and Z.-H. Zhou, ``Isolation Forest,'' in \textit{2008 IEEE International Conference on Data Mining}, pp. 413--422, 2008.

% Statistical Validation Methods
\bibitem{bland1986agreement}
J. M. Bland and D. G. Altman, ``Statistical methods for assessing agreement between two methods of clinical measurement,'' \textit{The Lancet}, vol. 327, no. 8476, pp. 307--310, 1986.

\bibitem{koo2016icc}
T. K. Koo and M. Y. Li, ``A Guideline of Selecting and Reporting Intraclass Correlation Coefficients for Reliability Research,'' \textit{Journal of Chiropractic Medicine}, vol. 15, no. 2, pp. 155--163, 2016.

\end{thebibliography}
\endgroup


\end{document}