\documentclass[../main.tex]{subfiles}

\begin{document}

    \addcontentsline{toc}{section}{ACKNOWLEDGEMENT}
    \section*{ACKNOWLEDGEMENT}
    
We take this opportunity to express our deepest and sincere gratitude to our Project Supervisor \textbf{ Er. Anisha Pokhrel} for her insightful advice, motivating suggestions, invaluable guidance, help and support in successful completion of this project and also for her constant encouragement and advice throughout our Bachelor's programme.
 
 We express our deep gratitude to \textbf{Er. Roshani Ghimire}, Head of Department,\textbf{ Dr.Raksha Dangol} and \textbf{Er. Navaraj Banstola}, Deputy Heads of Department of  Electronics and Computer Engineering for their regular support, co-operation, and coordination. The in-time facilities provided by the department throughout the Bachelors program are also equally acknowledgeable.
 
 We would like to express our thanks to the teaching and non-teaching staff of the Department of Electronics Communication and Computer Engineering, ACEM for their invaluable help and support throughout the period of the Bachelor’s Degree. We are also grateful to all our classmates for their help, encouragement and invaluable suggestions.
 
 Finally, yet more importantly, I would like to express our deep appreciation to my grandparents, parents, siblings for their perpetual support and encouragement throughout the Bachelor’s degree period.
  \\
    \vspace{0.1cm}
    
    \begin{table}[ht]
        \begin{tabular}{ll}
        Aayush Raj Nepal          & (\aayushroll)      \\
        Anurag Jha        & (\anuragroll)     \\
        Dipesh Bhatta         & (\dipeshroll)    \\
        Janak Acharya        & (\janakroll)\\
        \end{tabular}
    \end{table}
 
\end{document}

